Competing Bandits:\\The Perils of Exploration under Competition

### 2018-11-05 paper/competing_bandits.tex
Inserted a short/running title (without a line break).

\begin{document}
\title{Competing Bandits: \\ The Perils of Exploration under Competition}

@@

We ask whether better exploration algorithms are incentivized under competition. We run extensive numerical experiments in a stylized duopoly model in which two firms deploy multi-armed bandit algorithms and compete for myopic users.  We find that duopoly and monopoly tend to favor a primitive ``greedy algorithm" that does not explore \gaedit{and leads to low consumer welfare}, whereas a temporary monopoly (a duopoly with an early entrant) may incentivize better bandit algorithms \gaedit{and lead to higher consumer welfare. Our findings shed light on the first-mover advantage in the digital economy by exploring the role that data can play as a barrier to entry in online markets. We show that a data advantage may serve as a significant barrier to entry when exploration has significant reputational consequences for entrants.}
\end{abstract}

>>>>

\begin{document}
\title[Competing Bandits: The Perils of Exploration under Competition]
{Competing Bandits:\\The Perils of Exploration under Competition}

@@

We ask whether better exploration algorithms are incentivized under competition. We run extensive numerical experiments in a stylized duopoly model in which two firms deploy multi-armed bandit algorithms and compete for myopic users.  We find that duopoly and monopoly tend to favor a primitive ``greedy algorithm" that does not explore \gaedit{and leads to low consumer welfare}, whereas a temporary monopoly (a duopoly with an early entrant) may incentivize better bandit algorithms \gaedit{and lead to higher consumer welfare. Our findings shed light on the first-mover advantage in the digital economy by exploring the role that data can play as a barrier to entry in online markets. We show that a data advantage may serve as a significant barrier to entry when exploration has reputational consequences for entrants.}
\end{abstract}
